---
title: "10-import-hr-data"
output: html_notebook
---

# HR Data

IBM.HR Data-Employee-Attrition.xlsx is simulated data created by IBM to highlight the capabilities of their automated ML solutions. It is similar to HR retention data used by companies to analyze attrition (employees leaving the company). See https://www.kaggle.com/pavansubhasht/ibm-hr-analytics-attrition-dataset for full information.  

## Libraries

```{r}
library(tidyverse)
library(janitor)
library(h2o)
library(readxl)
library(glue)
library(lemon)
knit_print.data.frame <- lemon_print
library(knitr)
library(h2o)
h2o.init(nthreads = -1, #Number of threads -1 means use all cores on your machine
         max_mem_size = "8G")  #max mem size is the maximum memory to allocate to H2O
```
Open a browser to http://localhost:54321 to interact directly with H2O.



## Cost Data

In order to calculate the value of the model, we need to estimate the cost of retention, the cost of losing an employee, the probability of retention due to an intervention in the event attrition is predicted. 

```{r}
replace_multiplier <- 1.5 # Cost in multiple of annual salary to replace an employee
intervention_cost <- 1000  # Cost in dollars per person for retention program
success_rate <- .50       # Estimate success rate of retention program
```




## Read data

```{r}
attrition <- read_excel("data/IBM.HR Data-Employee-Attrition.xlsx", 
    col_types = c("numeric", "text", "text", 
        "numeric", "text", "numeric", "numeric", 
        "text", "numeric", "text", "numeric", 
        "text", "numeric", "numeric", "numeric", 
        "text", "numeric", "text", "numeric", 
        "numeric", "numeric", "text", "text", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric", 
        "numeric", "numeric", "numeric")) %>%
  clean_names() %>%
  select(attrition, everything(), -employee_number, -employee_count, -over18, -standard_hours) # Move target to front, remove unneeded
```

## Attrition Data Description


Name	Description
AGE	Numerical Value
ATTRITION	Employee leaving the company (0=no, 1=yes)
BUSINESS TRAVEL	(1=No Travel, 2=Travel Frequently, 3=Tavel Rarely)
DAILY RATE	Numerical Value - Salary Level
DEPARTMENT	(1=HR, 2=R&D, 3=Sales)
DISTANCE FROM HOME	Numerical Value - THE DISTANCE FROM WORK TO HOME
EDUCATION	Numerical Value
EDUCATION FIELD	(1=HR, 2=LIFE SCIENCES, 3=MARKETING, 4=MEDICAL SCIENCES, 5=OTHERS, 6= TEHCNICAL)
EMPLOYEE COUNT	Numerical Value
EMPLOYEE NUMBER	Numerical Value - EMPLOYEE ID
ENVIROMENT SATISFACTION	Numerical Value - SATISFACTION WITH THE ENVIROMENT
GENDER	(1=FEMALE, 2=MALE)
HOURLY RATE	Numerical Value - HOURLY SALARY
JOB INVOLVEMENT	Numerical Value - JOB INVOLVEMENT
JOB LEVEL	Numerical Value - LEVEL OF JOB
JOB ROLE	(1=HC REP, 2=HR, 3=LAB TECHNICIAN, 4=MANAGER, 5= MANAGING DIRECTOR, 6= REASEARCH DIRECTOR, 7= RESEARCH SCIENTIST, 8=SALES EXECUTIEVE, 9= SALES REPRESENTATIVE)
JOB SATISFACTION	Numerical Value - SATISFACTION WITH THE JOB
MARITAL STATUS	(1=DIVORCED, 2=MARRIED, 3=SINGLE)
MONTHLY INCOME	Numerical Value - MONTHLY SALARY
MONTHY RATE	Numerical Value - MONTHY RATE
NUMCOMPANIES WORKED	Numerical Value - NO. OF COMPANIES WORKED AT
OVER 18	(1=YES, 2=NO)
OVERTIME	(1=NO, 2=YES)
PERCENT SALARY HIKE	Numerical Value - PERCENTAGE INCREASE IN SALARY.
The parentage of change in salary between 2 year (2017, 2018).
PERFORMANCE RATING	Numerical Value - ERFORMANCE RATING
RELATIONS SATISFACTION	Numerical Value - RELATIONS SATISFACTION
STANDARD HOURS	Numerical Value - STANDARD HOURS
STOCK OPTIONS LEVEL	Numerical Value - STOCK OPTIONS.
How much company stocks you own from this company
TOTAL WORKING YEARS	Numerical Value - TOTAL YEARS WORKED
TRAINING TIMES LAST YEAR	Numerical Value - HOURS SPENT TRAINING
WORK LIFE BALANCE	Numerical Value - TIME SPENT BEWTWEEN WORK AND OUTSIDE
YEARS AT COMPANY	Numerical Value - TOTAL NUMBER OF YEARS AT THE COMPNAY
YEARS IN CURRENT ROLE	Numerical Value -YEARS IN CURRENT ROLE
YEARS SINCE LAST PROMOTION	Numerical Value - LAST PROMOTION
YEARS WITH CURRENT MANAGER	Numerical Value - YEARS SPENT WITH CURRENT MANAGER



