---
title: "40-modeling"
output: html_notebook
---

# Modeling

We'll be using H2O to provide high-speed model solutions and interactive model exploration. 

## Prepare data

We'll add features to the dataset based on the ideas from the group. 

```{r}
attrition_fe_csv <- "attrition_fe.csv"

attrition_fe <- attrition %>%
  select(everything()) %>%  # Remove unneeded features here to improve model
  years_in_current_role_rel_department() %>%
  write_csv(attrition_fe_csv) # Add feature functions in pipeline
```

*Cut and paste the section below to the Future Work slide*

## Future Work




## Run models

We'll call H2O, split the data, and run models. We'll simplify by applying just Random Forest models, and a GLM to examine contribution of specific levels of factors of variables. 


```{r}
data <- h2o.importFile(attrition_fe_csv)
data$attrition <- as.factor(data$attrition)  #encode the binary repsonse as a factor
h2o.levels(data$attrition)
y <- "attrition"
x <- setdiff(names(attrition_fe), c(y))

```

## Split data

Partition the data into training, validation and test sets

```{r}
splits <- h2o.splitFrame(data = data, 
                         ratios = c(0.7),  #partition data 
                         seed = 1)         #setting a seed will guarantee reproducibility
train <- splits[[1]]
valid <- splits[[2]]
```

## Run models

```{r}
rf_fit2 <- h2o.randomForest(x = x,
                            y = y,
                            training_frame = train,
                            model_id = "rf_fit2",
                            #validation_frame = valid,  #only used if stopping_rounds > 0
                            ntrees = 100,
                            seed = 1)
```


## Calculate value

Given the estimates from the attendees in the earlier session, determine what the value of solution would have been had we had it in place over the time represented in the data. 


```{r render=lemon_print}
attrition_salary <- attrition_fe %>%
  select(attrition, hourly_rate) %>% # Need only these fields for cost calcs
  mutate(
    annual_salary = 2080 * hourly_rate,  
  ) 

attrition_predict <- as.data.frame(h2o.predict(rf_fit2, data)) # Predict entire dataset (note that we are not using out-of-bag samples)

outcomes <- 
  cbind(attrition_salary, attrition_predict) %>% # Predict uses position only
  mutate(replace_cost = if_else(attrition == "Yes", replace_multiplier * annual_salary, 0),
         expected_cost_model = case_when(
           attrition == "Yes" & predict == "Yes" ~ replace_cost * (1-success_rate), # hit
           attrition == "Yes" & predict == "No"  ~ replace_cost,                    # miss
           attrition == "No"  & predict == "Yes" ~ intervention_cost,               # false alarm
           attrition == "No"  & predict == "No"  ~ 0                                # true no
           ),
         retain_prob = if_else(attrition == "Yes" & predict == "Yes", success_rate, 0)
         ) %>%
  summarise(no_model_cost = sum(replace_cost), 
            model_cost = sum(expected_cost_model), 
            retained = sum(retain_prob)) 

savings <- (outcomes$no_model - outcomes$model)/1000000

glue('\n\n\nModel Performance')
glue('\n\nModel would have saved ${format(savings, digits = 4, nsmall = 2)}M')
glue('Employees retained that would have been lost: {format(outcomes$retained, digits = 1, nsmall = 0)}\n\n')
```
Starting Model Performance

Model would have saved $20.37M
Employees retained that would have been lost: 60



## Find Top Predictors

```{r render=lemon_print}
h2o.varimp(rf_fit2) %>%
  select(variable, scaled_importance) %>%
  mutate(scaled_importance = round(scaled_importance, 2)) %>%
  head(10) %>%
  kable()

```

*Note on calculating expected value*
The prediction for each employee comes with a probability which can be read as the probability an employee just like this one will leave. 
